---
output: html_document
---
###**Multiple Regression Analysis** 
  _Yuyu Zhang_

####**Abstract**
In this report we extend the _simple regression analysis_ from last time and try to reproduce the main results displayed in section 3.2 _Multiple Linear Regression_ of the book  **An introduction to statistical Learning **

####**Introduction**
The goal is to extend the analysis of advertising data to see, besides TV, if other two medias newspaper and radio have an effect on the sales of a particular product. And if so, develop an accurate model that can be used to predict sales on the basis of three media budgets. 

####**Data**
The Advertising data set consists of the **Sales** (in thousands of units) of a particular product in 200 different
markets, along with advertising budgets (in thousands of dollars) for the product in each of those markets for
three different media: **TV,** **Radio**, and **Newspaper**.

####**Methodology**
The multiple linear regression model gives each predictor a separate slope coefficient in a single model:
       $$Sales=\beta_0+\beta_1TV+\beta_2Radio+\beta_3Newspaper$$
       
To estimate each coefficient we fit a regression model via the least square criterion.  For RSE, R squared and F-statistics we used the formulas in the book to carry computation.
  
####**Results**
The simple linear regression model for each media is shown in the tables below:
```{r,echo=FALSE, results="asis", comment=FALSE}
 dat<-read.csv("../data/Advertising.csv",row.names=1)
 reg_tv<-lm(Sales~TV, data=dat)
 library(xtable)
 
 reg_tv_coe<-summary(reg_tv)$coefficients
 reg_tv_table<-xtable(reg_tv_coe,caption="Table 1: Simple Regression of Sales on TV",digits=2,floating=FALSE)
 print(reg_tv_table, caption.placement = "top",type="html",output="report.html")
 cat("\n\n")
 
 reg_radio<-lm(Sales~Radio, data=dat)
 reg_radio_coe<-summary(reg_radio)$coefficients
 reg_radio_table<-xtable(reg_radio_coe,caption="Table 2: Simple Regression of Sales on Radio",digits=2,floating=FALSE)
 print(reg_radio_table, caption.placement = "top",type="html",output="report.html")
 cat("\n\n")
 
 reg_np<-lm(Sales~Newspaper, data=dat)
 reg_np_coe<-summary(reg_np)$coefficients
 reg_np_table<-xtable(reg_np_coe,caption="Table 3: Simple Regression of Sales on Newspaper",digits=2,floating=FALSE)
 print(reg_np_table, caption.placement = "top",type="html",output="report.html")
 cat("\n\n")
 
```

Coefficient estimates of the least squares model is shown below:
```{r,echo=FALSE, results="asis", comment=FALSE}
   load("../data/regression.RData")
   library(xtable)
   reg_table<-xtable(summary(mul_reg)$coefficients,caption="Table 3:Coefficient estimates of the least squares model",digits=4,floating=FALSE)
   print(reg_table,caption.placement = "top",type="html",output="report.html")
   
```
Correlation matrix of three medias and sales is summarized in the table below:
```{r,echo=FALSE, results="asis", comment=FALSE}
   load("../data/correlation-matrix.RData")
   library(xtable)
   cor_table<-xtable(matrix,caption="Table 4: Correlation matrix of TV, radio, newspaper and sales",digits=4,floating=FALSE)
   print(cor_table, caption.placement = "top",type="html",output="report.html")
   cat("\n\n")   
```

Lastly, RSE, R square and F-statistic of the least square model is summarized in the table below:
```{r,echo=FALSE, results="asis", comment=FALSE}
   load("../data/regression.RData")
   source("../code/functions/regression-functions.R")
  stats<-data.frame(Quantity=c("Residual standard error","R squared","F-statistic"),
            Value=c(residual_std_error(mul_reg),r_squared(mul_reg),f_statistic(mul_reg)) )
  stat_table<-xtable(stats,caption="Table 5:Other Relationship Statistics",digits=4,floating=FALSE)
  print(stat_table,caption.placement="top",type="html",output="report.html")
 
    # Quantity                Value
#-----------------------|-------
#Residual Standard Error| summary(mul_reg)$sigma
#R-squared              | summary(mul_reg)$r.squared
#F-statistic            | summary(mul_reg)$fstatistic
    cat("\n\n")
```
<hr>
Answers to additional questions:
* By looking at F-statistic, we can see if there's relationship between the response and predictors. Since the F-statistics from multiple regression model is 570>1, it means that at least one of the media is related to the sale

*  Only a subset of predictors are helpful

*  Combining R square, RSE and p-value, we conclude that a model that uses TV and radio expenditures to
predict sales is substantially better than one that uses only TV advertising. Adding newspaper almost have no effects on the product sales.

* We would use both 95% confidence interval and prediction interval to quantify the uncertainty.  The prediction
interval is substantially wider than the confidence interval, reflecting the increased uncertainty about sales for a given city in comparison to the average sales over many locations.


####**Conclusions**
In conclusion,  we used multiple regression models to visualize the relationship between  three advertising medias and their effects on product sales. The analysis suggests that a model with TV and radio as predictors are the more suitable one while newspaper has negligible effects on the product sales
  
